---
title: "homwork4_Sangwon Chung"
author: "Sangwon Chung"
date: "11/7/2019"
output: pdf_document
---


#1
```{r}
library(vcd)
site = matrix(c(22,2,10,16,54,115,19,33,73,11,17,28),byrow=TRUE,ncol=3)
colnames(site) = c("h","t","e")
row.names(site) = c("H","S","N","I")
names(dimnames(site)) = c("histological","site of tumor")
mosaic(site,main="site",shade = TRUE,color=TRUE)
library(ca)
plot(ca(site),labels=2)
legend(legend=names(dimnames(site)),x="bottomleft",col=c("blue","red"),pch=c(16,17))
```

#2
```{r}
species = read.csv("species.csv",header=TRUE,row.names =1)
colnames(species) = 1:17
library(ca)
plot(ca(species))
legend(legend=c("species","quadrats"),x="bottomleft",col=c("blue","red"),pch=c(16,17))
```

 
It is obvious that the quadrats with close numbers are similar to each other. Which means, they have similar features with respect to the number of different species. To be specific, the 1st, 2nd, 3rd and the 4th quadrats are highly positively correlated.  
The growing enviornment of the species which are close to each other in the plot such as *Festuca ovina*, *Plantago lanceolata*, *Hieracium pilosella* and *Achillea millefolium* are similar.  
The quadrats points which are close to one species point indicate their combination occurs more frequently than would be expected under the independence model. For instance, *Hieracium pilosella* grows most in the 1st quadrats.  

