---
title: "HW4 STAT424"
author: "Sangwon Chung"
date: "3/6/2018"
output:
  word_document: default
  html_document: default
---

Problem 1 

```{r}
library(readxl)
Girder_Data <- read_excel("/Users/user/Desktop/project/Girder Data.xlsx")
View(Girder_Data)
Gdat = stack(Girder_Data)
block = rep(c("b1","b2","b3","41","b5","b6","b7","b8","b9"),4)
Gdat = cbind(Gdat,block)
plot(lm(values~ind+block,data=Gdat))
summary(lm(values~ind+block,data=Gdat))
```

## Looking the first plot ("Residuals vs Fitted"), we can check that the red line 
## is not contant and the residuals cannot be represented as normal distribution 
## because the dots on the graph are not linearly connected in the second plot ("Normal Q-Q")

Problem 2

```{r}
TukeyHSD(aov(values~ind+block,data=Gdat),conf.level=0.99)$ind
```

## Compared to the result from in Section 3.2 at the 0.05 level, Tukey multiple comparisons at the 
## 0.01 level for the girder experiment have different intervals. Although p-adjusted values are not changed, each multiple comparison
## intervals are more extended than those at the 0.05 level.

# Problem 3

(a)

lock_df = 3-1 = 2 
block_MSS = 520/(3-1)= 260 
Trt_df = 5-1 = 4 
Trt_MSS = 498/(5-1) = 124.5 
Res_df = (3-1)(5-1)
Res_MSS = 40/8 = 5

# If design is not balanced, we cannot complete the ANOVA table

```{r}
my_tukey_block <- function(mean_1,mean_2,n_1,n_2,sigma_hat,df1,df2,alpha=0.01) {
diff = mean_2-mean_1
len = qtukey(p=1-alpha, nmeans=df1, df=df2)/sqrt(2)*sigma_hat*sqrt(1/n_1+1/n_2)
return(c(diff,diff-len,diff+len)) 
}

my_mean = c(45,58,46,45,56)
sigma_hat = sqrt(5)
b=3
k=5
tukey_result = matrix(0,10,3)
count=1
for(i in 1:4){
  for(j in (i+1):5){
    tukey_result[count,] = my_tukey_block(my_mean[i],my_mean[j],b,b,sigma_hat,k,(b-1)*(k-1))
    count = count+1
  }
  
}
```
###
(a)
```{r}
b=3
t=5
n=15
ssb=520
sst=498
sse=40
sst=ssb+sst+sse
dft=t-1
dfb=b-1
dfe=n-t-b+1
mst=sst/dft
msb=ssb/dfb
mse=sse/dfe

df=c(dfb,dft,dfe,"14")
ss=c(ssb,sst,sse,sst)
ms=c(msb,mst,mse," ")
ano=cbind(df,ss,ms)
```
(b)

```{r}
tukeyblock=function(mean.1,mean.2,n.1,n.2,sighat,df1,df2,alpha=0.01){
  diff=mean.2-mean.1
  len=qtukey(p=1-alpha,nmeans=df1,df=df2)/sqrt(2)*sighat*sqrt(1/n.1+1/n.2)
  return(c(diff,diff-len,diff+len))
}
mn=matrix(c(45,58,46,45,56))
sigmahat=sqrt(5)
b=3
k=5
tukey_result=matrix(0,10,3)
count=1
for(i in 1:4){
  for(j in (i+1):5){
    tukey_result[count,]=tukeyblock(mn[i],mn[j],b,b,sigmahat,k,(b-1)*(k-1))
    count=count+1
  }
  
}
tukey_result
sig=sqrt(40)
b=3
tt=matrix(numeric(0),nrow=5,ncol=5)
ttt=abs(qt(0.01/(6*2),8))
for(i in 1:4){
  for(j in (i+1):5){
    tt[j,i]=(mn[j,1]-mn[i,1])/(sig*sqrt(2/b))
    tt[i,i]=0
  }
}
tt
for(i in 1:4){
  for(j in (i+1):5){
    if(tt[j,i]<ttt){
      tt[j,i]=0
    }
  }
}
tt
cat("By looking at the chart, we could not find the pair that has bigger t statistic than our critical value 4.6308")
```


###

# Problem 4

```{r}
library(readxl)
Chemical_Reaction_Experiment <- read_excel("/Users/user/Desktop/project/Chemical Reaction Experiment.xlsx")
View(Chemical_Reaction_Experiment)
```

(a)

### As the chemical reaction experiment was carried out into two different portions
### to catalyst A and B, we need to use paired group test

(b)
```{r}
catalyst_A =c(9,19,28,22,18,8) 
catalyst_B =c(10,22,30,21,23,12)
t = t.test(catalyst_B, catalyst_A, paired=TRUE, alt = "greater",conf.level = 0.05)
L=length(catalyst_A)
d=numeric(length(catalyst_A))
for(i in 1:length(catalyst_A)){
  d[i]=catalyst_B[i]-catalyst_A[i]
}
mean.d=mean(d)
d2=numeric(length(catalyst_A))
for(i in 1:length(catalyst_A)){
  d2[i]=(d[i]-mean.d)^2
}
sigma.d=sqrt(sum(d2)/(L-1))
tt=mean.d/sigma.d*(sqrt(L))
tt
```
(c)
```{r}
Confidence.int=c(mean.d-(abs(qt(0.025,11))*(sigma.d)),mean.d+(abs(qt(0.025,11))*(sigma.d)))
Confidence.int
```
# Problem 5



# Problem 6

```{r}
y11 = c(20,16,17,18,15,16,19,14,15,24)
y12 = c(26,40,28,38,38,30,26,38,45,38)
y13 = c(25,40,30,17,16,45,49,33,30,20)
y21 = c(24,18,17,17,15,23,14,18,12,11)
y22 = c(32,22,30,35,32,28,27,28,30,30)
y23 = c(10,13,17,16,15,14,11,14,15,16)

s11 = log(var(y11))
s12 = log(var(y12))
s13 = log(var(y13))
s21 = log(var(y21))
s22 = log(var(y22))
s23 = log(var(y23))

y = c(s11,s12,s13,s21,s22,s23)
x1 = c(rep("Bolt",3),rep("Mandrel",3))
x2 = rep(c("CW","HT","PO"),2)
summary(aov(lm(y~x1+x2)))
```


